Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-03 analysis/paper/paper.Rmd
Remove redundant text
Remove more redundant text

Plant pathologists often provide information on protocols and chemicals allowing for reproducibility.
However, biological specimens such as strains, cultures or cultivars are often not available after publication.
These cases do constitute a lack of reproducibility but will not be covered here.

@@

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 were used to predict responses with publishing journal, using a factor, the journals' abbreviation, as the predictor (formula: response \~ abbreviation).
Models 3 and 4 were used to predict the two responses with a continuous value, year, as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)) to detect changes that occurred over the years in which the manuscripts were published that were included.
Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) and included assignee as random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.

>>>>

@@

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 were used to predict responses with publishing journal, using a factor, the journals' abbreviation, as the predictor (formula: response \~ abbreviation).
Models 3 and 4 were used to predict the two responses with a continuous value, year, as the predictor (formula: response \~&nbsp;year) and the models included abbreviation and assignee as random effects (formula: list(\~1&nbsp;\|&nbsp;abbreviation,&nbsp;\~1&nbsp;\|&nbsp;assignee)) to detect changes that occurred over the years in which the manuscripts were published that were included.
Models 5 and 6 were used to predict the responses using a continuous value, IF_5year, as the predictor, (formula: response&nbsp;\~&nbsp;IF_5year) (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
All models included the assigned article evaluator as a random effect (formula:&nbsp;\~1&nbsp;\|&nbsp;assignee) to address inter-rater effects on scoring.
